Source Summaries

### 2020-04-12 paper/sourceSummaries/summary8.tex
summary 8 initial commit

@@

@@

@@

@@

@@

@@

>>>>

\noindent
\subsection{{BLE} {B}roadcasting {I}mpact in a {R}eal {N}etwork {E}nvironment}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{boric2017ble}

@@

\noindent
The Authors examine the traffic sent by individual BLE devices to determine the impact these devices can have on latency in a simulation production environment. They also do tests to determine whether or not broadcast advertisement length has any effect on message delivery.

@@

\noindent
The authors use Scientific Theory to observe and explain the outcome of the experiment following numerous tests adhering to the scientific method.

@@

\noindent
A Raspberry Pi 2 Model B was used as the base testing hardware for this experiment. In order to achieve the results that they did, the authors also had to equip the device with a Bluefruit LE Sniffer and some specific Bluetooth libraries that are not supported out of the box by raspberry pi (libdbus-1-dev,  libdbus-glib-1-dev,  libglib2.0-dev,  libical-dev, libreadline-dev, libudev-dev, libusb-dev)

@@

\noindent
The authors found that the neither the duration of advertisement nor the distance between the advertiser and the collector affect the I/O capabilities of the advertiser if it is alone on the network. However, signs of latency began to show themselves while testing a broadcast with 10 other devices on the network.

@@

\noindent
The authors suggest future work would include testing advertisement capabilities of devices moving around on the network since they were only testing static location. They also suggest testing of a more device dense enviroment to see how the pattern they identified grows with more devices.
